Untitled

### 2014-12-03 GEMDataSource.Rmd
Edit Zelig sim and write csv of WayofTeaching Data

@@

# Run linear regression R1
R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeach + Country, data = CompleteData)

@@

# Run linear regression R2
R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeach + Country, data = CompleteData)

@@

# Run linear regression R3
R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeach + Country, data = CompleteData)

>>>>

write.csv(subW2, file = "WayofTeaching")

@@

# Run linear regression R1
R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeaching, data = CompleteData)

@@

# Run linear regression R2
R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeaching, data = CompleteData)

@@

# Run linear regression R3
R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeaching, data = CompleteData)

### 2014-12-03 Presentation/EdEntrePres.Rmd
Edit Zelig sim and write csv of WayofTeaching Data

@@

D4 %>% ggvis(~mean, fill := "#2c7fb8") %>% layer_histograms(width = 0.2)

@@

# Library stargazer
library(stargazer)

# Create new DF for PerceivedOpportunities
D5 <- PerceivedOpportunities

# Eliminate X's in header
names(D5) <- gsub("X", "", names(D5))  
D5$new.col <- NULL

# Create descriptive statistics table
T1 <- stargazer(D5, type = 'html', column.sep.width = "20pt", digits = 2)
```
## Slide with Plot

@@

# Run a RE regression
Z1 <- zelig(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeach, data = CompleteData_omit, model = "ls")

>>>>

# Save cleaned df
Opp1 <- D4

@@

line_plot <- gvisLineChart(Opp1)
print(line_plot, tag = 'chart')

@@

## WayofTeaching
```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
# Import GEM data frame
WayofTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv", header = TRUE, cache = FALSE, na.strings = "-")

# Drop unnecessary column 1
WayofTeaching$X <- NULL

## Slide with Plot

@@

# Run a RE regression
Z1 <- zelig(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeaching, data = CompleteData_omit, model = "ls")

### 2014-12-03 Presentation/PresMisc/MiscPresStuff.Rmd
Edit Zelig sim and write csv of WayofTeaching Data

>>>>

```{r}
# Histogram
D4 %>% ggvis(~mean, fill := "#2c7fb8") %>% layer_histograms(width = 0.2)

# Library stargazer
library(stargazer)

# Create new DF for PerceivedOpportunities
D5 <- PerceivedOpportunities

# Eliminate X's in header
names(D5) <- gsub("X", "", names(D5))  
D5$new.col <- NULL

# Create descriptive statistics table
T1 <- stargazer(D5, type = 'html', column.sep.width = "20pt", digits = 2)
